Optimal Algorithms for Dynamic Balanced Graph Partitioning

### 2020-05-14 paper/disc20clustering.tex
correcting ground set def (1)
tikz

Given a perfect partition,
every subset of nodes that belong to the same cluster in this partition
is a~\emph{ground set}. 
On each inter-cluster request a ground set is revealed.
Any competitive algorithm under the learning model,
 maintains a~perfect partition of ground sets into clusters.
 An algorithm recovers the (hidden) perfect partition gradually over inter-cluster requests,
  by merging pairs of ground sets involved in these requests.

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.4\textwidth]{figs/cyclic}
	\caption{
		\OPT  collocates 5 pairs, paying one migration per pair.
	Dashed lines represent requests.
	An arrow, e.g.~from $b_1$ to $a_1$ means  that $b_1$ replaces $a_1$.\maciek{Maybe: "An arrow from $a$ to $b$ means that $b$ replaces $a$.". Or "$b$ migrates in place of $a$."} }
	\label{fig:cyclic}
\end{figure}

>>>>

Given a perfect partition,
every subset of nodes that belong to the same cluster in this partition
is a~\emph{ground set}. 
Any competitive algorithm under the learning model,
 maintains a~perfect partition of ground sets into clusters.
 On each inter-cluster request a ground set is revealed.
 An algorithm recovers the (hidden) perfect partition gradually over inter-cluster requests,
  by merging pairs of ground sets involved in these requests.

@@

\begin{figure}[H]
	\centering
\begin{minipage}{.5\textwidth}
	\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1.25,xscale=1.25]
	\useasboundingbox  (-3mm,-5mm) rectangle (0mm,10mm);
	%cluster 1
	\def\x{30}
	\def\w{15}
	%Shape: Rectangle
	\draw   (0,0) -- (15,0) -- (15,40) -- (0,40) -- cycle ;
	%Straight Lines
	\draw   (0,20) -- (15,20) ;
	% Text Node
	\draw (8,10) node (b1)  {$b_{1}$} ;
	% Text Node
	\draw (8,30) node (a4)   {$a_{4}$};

	%cluster 2
	\draw   (\x,0) -- (\w+\x,0) -- (\w+\x,40) -- (\x,40) -- cycle ;
	\draw   (\x,20) -- (\w+\x,20) ;
	% Text Node
	\draw (\x+8,10) node (b2)   {$b_{2}$};
	% Text Node
	\draw (\x+8,30) node (a1)   {$a_{1}$};

	\draw[dotted, shorten <= -6pt, shorten >= -6pt] (a4)  -- (a1);
	\draw [->,blue, shorten <= -5pt, shorten >= -2pt] (a4) -- (b2);

	%cluster 3
	\draw   (2*\x,0) -- (\w+2*\x,0) -- (\w+2*\x,40) -- (2*\x,40) -- cycle ;
	\draw    (2*\x,20) -- (\w+2*\x,20) ;
	% Text Node
	\draw (2*\x+8,10) node (b3)   {$b_{3}$};
	% Text Node
	\draw (2*\x+8,30) node (a2)   {$a_{2}$};
	\draw[dotted, shorten <= -4pt, shorten >= -3pt] (b2)  -- (b3);
	\draw [->,blue, shorten <= -5pt, shorten >= -2pt] (b2) -- (a2);

	%cluster 4
	\draw   (3*\x,0) -- (\w+3*\x,0) -- (\w+3*\x,40) -- (3*\x,40) -- cycle ;
	\draw    (3*\x,20) -- (\w+3*\x,20) ;
	% Text Node
	\draw (3*\x+8,10) node (b4)   {$b_{4}$};
	% Text Node
	\draw (3*\x+8,30) node (a3)   {$a_{3}$};
	\draw[dotted, shorten <= -4pt, shorten >= -3pt] (a2)  -- (a3);
	\draw [->,blue, shorten <= -5pt, shorten >= -2pt] (a2) -- (b4);

	\draw[dotted,  shorten <= -3pt, shorten >= -5pt]  (b4) to[out=-100,in=-80] (b1);
	% arrow
	\draw[->, blue,shorten <= -3pt, shorten >= -4pt]  (b4) 
	to [out=-108,in=-130, distance=17mm]  (a4);
	\end{tikzpicture}
\end{minipage}\hfill
%
\begin{minipage}{.5\textwidth}
	\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1.25,xscale=1.25]
	\useasboundingbox  (0mm,-5mm) rectangle (0mm,10mm);
%cluster 1
\def\x{30}
\def\w{15}
%Shape: Rectangle
\draw   (0,0) -- (15,0) -- (15,40) -- (0,40) -- cycle ;
%Straight Lines
\draw   (0,20) -- (15,20) ;
% Text Node
\draw (8,10) node (b1)  {$b_{1}$} ;
% Text Node
\draw (8,30) node (b4)   {$b_{4}$};

%cluster 2
\draw   (\x,0) -- (\w+\x,0) -- (\w+\x,40) -- (\x,40) -- cycle ;
\draw   (\x,20) -- (\w+\x,20) ;
% Text Node
\draw (\x+8,10) node (a4)   {$a_{4}$};
% Text Node
\draw (\x+8,30) node (a1)   {$a_{1}$};

%cluster 3
\draw   (2*\x,0) -- (\w+2*\x,0) -- (\w+2*\x,40) -- (2*\x,40) -- cycle ;
\draw    (2*\x,20) -- (\w+2*\x,20) ;
% Text Node
\draw (2*\x+8,10) node (b3)   {$b_{3}$};
% Text Node
\draw (2*\x+8,30) node (b2)   {$b_{2}$};

%cluster 4
\draw   (3*\x,0) -- (\w+3*\x,0) -- (\w+3*\x,40) -- (3*\x,40) -- cycle ;
\draw    (3*\x,20) -- (\w+3*\x,20) ;
% Text Node
\draw (3*\x+8,10) node (a2)   {$a_{2}$};
% Text Node
\draw (3*\x+8,30) node (a3)   {$a_{3}$};
\end{tikzpicture}
\end{minipage}
	\caption{
			Dashed lines represent requests.
		An arrow from node $x$ to node $y$ indicates that $x$  replaces $y$.
		\OPT collocates 4 pairs from the left partition, with  4 migrations,
		 resulting in the right partition.
	}
	\label{fig:cyclic}
\end{figure}
